Multi-line Intensity Mapping

### 2019-07-15 paper/ms.tex
Small update
Expand on noise section

In
order to compute the covariance matrix, we use the result that \citep[e.g.][]{2010JCAP...11..016V},
\beq\label{eq:var_cov}
\begin{split}
\Var{\xps{i}{j}} &= \xps{i}{j}^2 + \pstot{i}\pstot{j} \\
\Cov{\xps{i}{j}}{\xps{i}{k}} &= \pstot{i}\xps{j}{k} +
\xps{i}{j}\xps{i}{k}\text{,}
\end{split}
\eeq
where $\pstot{i} = \ps{i} + N_i$. Note that $N_i$ contains contributions from
instrument noise, residual foreground contamination, and
interloping/extraloping lines.

\subsection{Noise Components}\label{ssec:noise}
We describe the implementation of each noise component.

\subsubsection{Interloping and Extraloping Lines}\label{sssec:interlopers}

@@

Inverting this matrix we find that the covariance matrix of the bias factors is,
\beq \label{eq:covmat_tf_wn}
C = F^{-1} = \frac{1}{4V_k^2}
\begin{pmatrix}
\frac{B_1^2N_2N_3 + B_2^2N_3N_1 + B_3^2N_1N_2}{B_2^2B_3^2} & \frac{-B_1^2N_2N_3 - B_2^2N_3N_1 + B_3^2N_1N_2}{B_1B_2B_3^2} & \frac{-B_1^2N_2N_3 + B_2^2N_3N_1 - B_3^2N_1N_2}{B_1B_2^2B_3} \\
\frac{-B_1^2N_2N_3 - B_2^2N_3N_1 + B_3^2N_1N_2}{B_1B_2B_3^2} & \frac{B_1^2N_2N_3 + B_2^2N_3N_1 + B_3^2N_1N_2}{B_3^2B_1^2} & \frac{B_1^2N_2N_3 - B_2^2N_3N_1 - B_3^2N_1N_2}{B_1^2B_2B_3} \\
\frac{B_1^2N_2N_3 - B_2^2N_3N_1 - B_3^2N_1N_2}{B_1^2B_2B_3} & \frac{B_1^2N_2N_3 - B_2^2N_3N_1 - B_3^2N_1N_2}{B_1^2B_2B_3} & \frac{B_1^2N_2N_3 + B_2^2N_3N_1 + B_3^2N_1N_2}{B_1^2B_2^2}
\end{pmatrix}
\text{.}
\eeq
Examining the diagonal components we have that:
\beq \label{eq:var_bias_tf_wn}
\begin{split}
C_{1,1} = \sigma_{B_1}^2 &= \frac{1}{4V_k^2} \left( B_1^2 \frac{N_2N_3}{B_2^2B_3^2} + N_1(\frac{N_2}{B_2^2} + \frac{N_3}{B_3^2}) \right) \\
\implies \frac{\sigma_{B_1}^2}{B_1^2} &= \frac{1}{4V_k^2} \left( \frac{N_1N_2}{B_1^2B_2^2} + \frac{N_2N_3}{B_2^2B_3^2} + \frac{N_3N_1}{B_3^2B_1^2} \right)\text{.}
\end{split}
\eeq
The symmetry of this result implies that,
\beq \label{eq:frac_error_same}
\frac{\sigma_{B_1}}{B_1} = \frac{\sigma_{B_2}}{B_2} = 
\frac{\sigma_{B_3}}{B_3}\text{.}
\eeq
Unfortunately the surprising result that the fractional error on each line is
the same only holds in the three field case.

>>>>

In
order to compute the covariance matrix, we use the result that \citep[e.g.][]{2010JCAP...11..016V},
\beq\label{eq:var_cov}
\begin{split}
\Var{\xps{i}{j}} &= \xps{i}{j}^2 + \pstot{i}\pstot{j} \\
\Cov{\xps{i}{j}}{\xps{i}{k}} &= \pstot{i}\xps{j}{k} +
\xps{i}{j}\xps{i}{k}\text{,}
\end{split}
\eeq
where $\pstot{i} = \ps{i} + N_i$. The computation of the noise $N_i$ is given in the next subsection.

\subsection{Noise Components}\label{ssec:noise}
We describe the computation of each noise component. In principle the noise
should consist of three components:
\beq\label{eq:noise_comp}
N_i = N_{i,\text{instrumental}} + N_{i,\text{interlopers}} + N_{i,\text{foreground}}\text{.}
\eeq
However, in this work we will ignore the foreground contribution. Our work
should then be seen as a best-case scenario. {\bf add more words}

\subsubsection{Instrumental Noise}\label{sssec:instrumental}
{\bf Add.}

\subsubsection{Interloping and Extraloping Lines}\label{sssec:interlopers}
The noise for interloping and extraloping lines can be written as
\citep{2016ApJ...825..143L, 2016ApJ...832..165C},
\beq\label{eq:ptot_intlpr}
N_{i,\text{interlopers}} = \sum_{j} \frac{1}{\apar(z_j) \aperp(z_j)^2} 
            P_j\left(\frac{\kpar}{\apar(z_j)}, 
                     \frac{\kperp}{\aperp(z_j)}\right)\text{,}
\eeq
where the sum on $j$ is over all interloping lines, $z_j$ is the
emitted redshift of line $j$, and where,
\begin{alignat}{2}
\apar = \frac{H(z_i)}{H(z_j)} \frac{1+z_j}{1+z_i} \quad \quad &&
\aperp = \frac{D_{A}(z_j)}{D_A(z_i)}\text{,}
\end{alignat}
where $z_i$ is the emitted redshift of line $i$ and $D_A(z)$ is the comoving
angular diameter distance to redshift $z$.

@@

Inverting this matrix we find that the covariance matrix of the bias factors is,
\beq \label{eq:covmat_tf_wn}
C = F^{-1} = \frac{1}{4V_k^2}
\begin{pmatrix}
\frac{B_1^2N_2N_3 + B_2^2N_3N_1 + B_3^2N_1N_2}{B_2^2B_3^2} & \frac{-B_1^2N_2N_3 - B_2^2N_3N_1 + B_3^2N_1N_2}{B_1B_2B_3^2} & \frac{-B_1^2N_2N_3 + B_2^2N_3N_1 - B_3^2N_1N_2}{B_1B_2^2B_3} \\
\frac{-B_1^2N_2N_3 - B_2^2N_3N_1 + B_3^2N_1N_2}{B_1B_2B_3^2} & \frac{B_1^2N_2N_3 + B_2^2N_3N_1 + B_3^2N_1N_2}{B_3^2B_1^2} & \frac{B_1^2N_2N_3 - B_2^2N_3N_1 - B_3^2N_1N_2}{B_1^2B_2B_3} \\
\frac{B_1^2N_2N_3 - B_2^2N_3N_1 - B_3^2N_1N_2}{B_1^2B_2B_3} & \frac{B_1^2N_2N_3 - B_2^2N_3N_1 - B_3^2N_1N_2}{B_1^2B_2B_3} & \frac{B_1^2N_2N_3 + B_2^2N_3N_1 + B_3^2N_1N_2}{B_1^2B_2^2}
\end{pmatrix}
\text{.}
\eeq
Examining the diagonal components we have that:
\beq \label{eq:var_bias_tf_wn}
\begin{split}
C_{1,1} = \sigma_{B_1}^2 &= \frac{1}{4V_k^2} \left( B_1^2 \frac{N_2N_3}{B_2^2B_3^2} + N_1(\frac{N_2}{B_2^2} + \frac{N_3}{B_3^2}) \right) \\
\implies \frac{\sigma_{B_1}^2}{B_1^2} &= \frac{1}{4V_k^2} \left( \frac{N_1N_2}{B_1^2B_2^2} + \frac{N_2N_3}{B_2^2B_3^2} + \frac{N_3N_1}{B_3^2B_1^2} \right)\text{.}
\end{split}
\eeq
The symmetry of this result implies that,
\beq \label{eq:frac_error_same}
\frac{B_1}{\sigma_{B_1}} = \frac{B_2}{\sigma_{B_2}} = 
\frac{B_3}{\sigma_{B_3}} \text{.}
\eeq
Unfortunately the surprising result that the fractional error on each line is
the same only holds in the three field case.
